A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2023-08-06 pilot-publication/lab-book.Rmd
Add labels to synthetic data
Work to create and compare outcome tables
Update synthetic data

```{r setup}
library(pbapply)
library(openssl)
library(dotenv)
```

@@

>>>>

```{r setup}
library(pbapply)
library(openssl)
library(dotenv)
library(DataExplorer)
```

@@

## Put labels back
synth.data <- synth.data %>% labelled::copy_labels_from(data)

## Create data report
DataExplorer::create_report(synth.data, report_title = "Synthetic data report", output_file = "synth-data-report.html")
